Extracting Function Signature from R Program Traces

### 2020-05-14 paper/main.tex
merge

Of the remaining \~60\% of failed contract assertions, we found quite an interesting pattern: the top as-of-yet unexplained contract failure, making up roughly 7\% of total failed assertions, is an assertion checking a ${\bf character}$ against the expected type ${\bf class} \langle bignum \rangle \, | \, {\bf raw}[]$.

Separately, we investigated the effect of running reverse dependency code on the code coverage of the packages in our corpus.
Further investigation revealed that most failures were coming from the \code{openssl::base64_encode} function, whose code is available in Figure~\ref{fig:base64-encode}.

@@

>>>>

Of the remaining \~60\% of failed contract assertions, we found quite an interesting pattern: the top as-of-yet unexplained contract failure, making up roughly 7\% of total failed assertions, is an assertion checking a ${\bf character}$ against the expected type ${\bf class} \langle bignum \rangle \, | \, {\bf raw}[]$.
Further investigation revealed that most of these failures were coming from the \code{openssl::base64_encode} function, whose code is available in Figure~\ref{fig:base64-encode}.

@@

But what of the large amount (\~70\%) of assertion failures in functions with 100\% coverage?
As it happens, many of these functions have very few lines of code, many having as few as a single line.
The most interesting among these are functions which are the entry point for S3 dispatch (these functions typically have a single line of code, \code{UseMethod("InsertS3MethodNameHere")}).

It turns out that the lion's share of the remaining polymorphism is related to S3 dispatch.
S3 generics are naturally polymorphic, and we aim to define types to capture these cases, and implement a full-fledged object-oriented type system for R in future work.
In the meantime, if we count out S3 methods, we find that only \AT{few} contract failures remain.
